Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-14 paper/paper.tex
more on figs

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example1.png}
\caption{Spatial and group organization provided by subject 1.}
\label{fig:xp2display}
\end{figure}

@@

It may also be of interest to condition the space using the aggregate similarity judgments given by several subjects. We found that using a hypergraph partitioning algorithm \cite{kernighan1970efficient,han1997scalable,strehl2002cluster} to produce the consensus similarity matrix performed well.

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsI.png}
\caption{}
\label{fig:consensusVsI}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsPt.png}
\caption{ }
\label{fig:consensusVsPt}
\end{figure}

>>>>

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example1.png}
\caption{Spatial and group organization provided by subject 1\footnote{The organizations of the other subjects are available online \url{https://mathieulagrange.github.io/paperPlayingTechniquesSimilarityLearning/demo}. For each subject, the stimuli can be played back by hovering on the dots.}.}
\label{fig:xp2display}
\end{figure}

@@

In this study, we choose to condition the space using the aggregate similarity judgments given by several subjects. We found that using a hypergraph partitioning algorithm \cite{kernighan1970efficient,han1997scalable,strehl2002cluster} to produce the consensus similarity matrix performed well.

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsI.png}
\caption{Normalized similarity matrix of the consensus clustering aggregated by the musical instruments used. Ordering is chosen to maximize readability.}
\label{fig:consensusVsI}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsPt.png}
\caption{Normalized similarity matrix of the consensus clustering aggregated by the playing techniques used. Ordering is chosen to maximize readability.}
\label{fig:consensusVsPt}
\end{figure}
